%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Deep Learning in Ultrasound Imaging} % Role
    {Siemens Healthineers} % Event
    {Princeton, U.S.A} % Location
    {Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced Ultrasound imaging principles and applications.}
        \item {Introduced Universal Deep beamformer for Medical Ultrasound Imaging.}
        \item {Introduced Switchable and Tunable Beamformer.}
        \item {Introduced Variational formulation of unsupervised Deep learning for ultrasound image artifact removal.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Deep Learning for Efficient Ultrasound Imaging} % Role
    {Precision Electromedicince (KAIST Bio-IT Healthcare Initiative III Symposium)} % Event
    {Daejeon, S.Korea} % Location
    {Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced Ultrasound imaging principles and applications.}
        \item {Introduced Deep learning technologies.}
        \item {Introduced variable rate beamformer for Efficient Ultrasound Imaging.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Deep learning beamformer for variable rate ultrasound imaging} % Role
    {Wavelets and Sparsity XVIII. International Society for Optics and Photonics} % Event
    {San Diego, California, U.S.A} % Location
    {Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced Ultrasound imaging and Deep learning technologies.}
        \item {Introduced Mathematical Link between adaptive beamformer and deep learning.}
        \item {Introduced variable rate beamformer for Efficient Ultrasound Imaging.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
