%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publication Highlights}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\small
\subsection*{Patent Applications}
    \begin{enumerate}
    \item Ye, Jong Chul, \textbf{Shujaat Khan} and Jaeyoung Huh. "Apparatus and method for processing ultrasound image in various sensor conditions." \textit{\textbf{US Patent App. US16/721,015 - US20210030400A1}} \href{https://patents.google.com/patent/US20210030400A1/en}{[\textcolor{blue}{online}]}
    
    \item Ye, Jong Chul, \textbf{Shujaat Khan} and Jaeyoung Huh. "Method for processing ultrasound image in various sensor conditions and apparatus therefor (다양한 센서 조건에서의 초음파 영상 처리 장치 및 그 방법)." \textit{\textbf{KR Patent App. 1020190092146 (2019.07.30)}} \href{https://doi.org/10.8080/1020190092146?urlappend=en}{[\textcolor{blue}{online}]}
    
    \item Ye, Jong Chul, Yeo Hun Yoon, \textbf{Shujaat Khan} and Jaeyoung Huh. "Image processing apparatus using neural network and method performed by image processing apparatus." \textit{\textbf{US Patent App. 16/414,372 - US20190355093A1}} \href{https://patents.google.com/patent/US20190355093A1/en}{[\textcolor{blue}{online}]}
    \end{enumerate}

\subsection*{Journals}
\begin{enumerate}
    \item Abdul Wahab, \textbf{Shujaat Khan}, and Farrukh Zeeshan Khan. "Comments on 'Design of momentum fractional LMS for Hammerstein nonlinear system identification with application to electrically stimulated muscle model'." \textit{\textbf{European Physical Journal Plus}}, vol. XX, no. X, pp. XX, XX. 2021, (Accepted) \href{https://arxiv.org/pdf/2009.07076.pdf}{[\textcolor{blue}{online}]}

    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Variational Formulation of  Unsupervised Deep Learning for Ultrasound Image Artifact Removal." \textit{\textbf{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control}}, vol. 68, no. 6, pp. 2086-2100, June. 2021, \href{https://doi.org/10.1109/tuffc.2021.3056197}{[\textcolor{blue}{online}]}

    \item \textbf{Shujaat Khan}, Abdul Wahab, Imran Naseem and Muhammad Moinuddin . 'Comments on “Design of fractional-order variants of complex LMS and NLMS algorithms for adaptive channel equalization'." \textit{\textbf{Nonlinear Dynamics}}, 2020, \href{https://doi.org/10.1007/s11071-020-05850-w}{[\textcolor{blue}{online}]}

    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Adaptive and Compressive Beamforming Using Deep Learning for Medical Ultrasound." \textit{\textbf{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control}}, vol. 67, no. 8, pp. 1558-1572, Aug. 2020, \href{https://doi.org/10.1109/TUFFC.2020.2977202}{[\textcolor{blue}{online}]}
 
    \item Muhammad Usman, \textbf{Shujaat Khan}, and Jeong-A Lee. "AFP-LSE: Antifreeze Proteins Prediction Using Latent Space Encoding of Composition of k-Spaced Amino Acid Pairs." \textit{\textbf{Scientific Reports}} 10, 7197 (2020). \href{https://doi.org/10.1038/s41598-020-63259-2}{[\textcolor{blue}{online}]}
    
   \item Abdul Wahab, and \textbf{Shujaat Khan}. "Comments and Corrections Comments on 'Fractional Extreme Value Adaptive Training Method: Fractional Steepest Descent Approach'." \textit{\textbf{IEEE Transactions on Neural Networks and Learning Systems}}, vol. 31, no. 3, pp. 1066-1068, March 2020, \href{https://doi.org/10.1109/TNNLS.2019.2899219}{[\textcolor{blue}{online}]} 
    
    \item Alishba Sadiq, \textbf{Shujaat Khan}, Imran Naseem, Roberto Togneri, and Mohammed Bennamoun. "Enhanced q-least Mean Square." \textit{\textbf{Circuits, Systems, and Signal Processing}} 38, no.10 (2019): 4817-4839. \href{https://doi.org/10.1007/s00034-019-01091-4}{[\textcolor{blue}{online}]}
    
    \item Yeo Hun Yoon, \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Efficient b-mode ultrasound image reconstruction from sub-sampled rf data using deep learning." \textit{\textbf{IEEE Transactions on Medical Imaging}} 38, no. 2 (2019): 325-336. \href{https://doi.org/10.1109/TMI.2018.2864821}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Imran Naseem, Muhammad Ammar Malik, Roberto Togneri, and Mohammed Bennamoun. "A fractional gradient descent-based rbf neural network." \textit{\textbf{Circuits, Systems, and Signal Processing}} 37, no. 12 (2018): 5311-5332. \href{https://doi.org/10.1007/s00034-018-0835-3}{[\textcolor{blue}{online}]}
    
    \item Tasawar Abbas, \textbf{Shujaat Khan}, Muhammad Sajid, Abdul Wahab, Jong Chul Ye, “Topological sensitivity based far-field detection of elastic inclusions”, \textit{\textbf{Results in Physics}}, Volume 8, March 2018, Pages 442-460, ISSN 2211-3797. \href{https://doi.org/10.1016/j.rinp.2017.12.041}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Jawwad Ahmad, Imran Naseem, and Muhammad Moinuddin. "A Novel Fractional Gradient-Based Learning Algorithm for Recurrent Neural Networks." \textit{\textbf{Circuits, Systems, and Signal Processing}}  37, no. 2 (2018): 593-612. \href{https://doi.org/10.1007/s00034-017-0572-z}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Imran Naseem, Roberto Togneri, and Mohammed Bennamoun, "RAFP-Pred: Robust Prediction of Antifreeze Proteins Using Localized Analysis of n-Peptide Compositions" \textit{\textbf{IEEE/ACM Transactions on Computational Biology and Bioinformatics}}, vol. 15, no. 1, pp. 244-250, Jan.-Feb. 1 2018. \href{https://doi.org/10.1109/TCBB.2016.2617337}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Imran Naseem, Roberto Togneri, and Mohammed Bennamoun. "A Novel Adaptive Kernel for the RBF Neural Networks." \textit{\textbf{Circuits, Systems, and Signal Processing}}, 36, no. 4 (2017): 1639-1653. \href{https://doi.org/10.1007/s00034-016-0375-7}{[\textcolor{blue}{online}]}
    
    \item Imran Naseem, \textbf{Shujaat Khan}, Roberto Togneri, and Mohammed Bennamoun. "ECMSRC: A Sparse Learning Approach for the Prediction of Extracellular Matrix Proteins." \textit{\textbf{Current Bioinformatics}} 12 (2017): 361-368. \href{https://doi.org/10.2174/1574893611666151215213508}{[\textcolor{blue}{online}]}
\end{enumerate}

\subsection*{Selected Conferences}
\begin{enumerate}
    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Unsupervised Deep Learning for Accelerated High Quality Echocardiography." in  \textit{\textbf{2021-IEEE International Symposium on Biomedical Imaging (ISBI-2021)}}, Nice, France. \href{https://ieeexplore.ieee.org/document/9433770}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Switchable Deep Beamformer for Ultrasound Imaging Using AdaIN." in  \textit{\textbf{2021-IEEE International Symposium on Biomedical Imaging (ISBI-2021)}}, Nice, France. \href{https://ieeexplore.ieee.org/document/9433757}{[\textcolor{blue}{online}]}

    \item Seongyong Park, \textbf{Shujaat Khan}, Muhammad Moinuddin, Ubaid M. Al-Saggaf. "GSSMD: A new standardized effect size measure to improve robustness and interpretability in biological applications," in  \textit{\textbf{2020 IEEE International Conference on Bioinformatics and Biomedicine (BIBM)}}, Seoul, Korea (South), 2020, pp. 1096-1099, \href{https://ieeexplore.ieee.org/document/9313582}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Unsupervised Deconvolution Neural Network for High Quality Ultrasound Imaging," in  \textit{\textbf{2020 IEEE International Ultrasonics Symposium (IUS)}}, Las Vegas, NV, USA, 2020, pp. 1-4, \href{https://doi.org/10.1109/IUS46767.2020.9251418}{[\textcolor{blue}{online}]} \href{https://youtu.be/L_iEO24Vvrw}{[\textcolor{blue}{video}]}
    
    % \item Alishba Sadiq, Muhammad Usman, \textbf{Shujaat Khan}, Imran Naseem, Muhammad Moinuddin, and Ubaid M. Al-Saggaf. "q-lmf: Quantum calculus-based least mean fourth algorithm." In \textit{\textbf{Fourth International Congress on Information and Communication Technology, Springer}}, Singapore, 2020, pp. 303-311, \href{https://doi.org/10.1007/978-981-15-0637-6_25}{[\textcolor{blue}{online}]}

    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Universal Plane-Wave Compounding for High Quality US Imaging Using Deep Learning." in  \textit{\textbf{2019 IEEE International Ultrasonics Symposium (IUS)}}, Glasgow, United Kingdom, 2019, pp. 2345-2347, \href{https://doi.org/10.1109/ULTSYM.2019.8925679}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Jaeyoung Huh, Regev Cohen, Yonina Eldar and Jong Chul Ye. "Clutter Suppressed Deep Beamformer for Echocardiography using Deep Learning." in \textit{\textbf{2019 IEEE International Ultrasonics Symposium (IUS)}}, Glasgow, United Kingdom, 2019, \href{https://doi.org/10.13140/RG.2.2.15564.77443}{[\textcolor{blue}{online}]} [ABSTRACT-POSTER]
    
    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Deep Learning-based Universal Beamformer for Ultrasound Imaging." in \textit{\textbf{the 22nd International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI), \colorbox{yellow}{MICCAI 2019}. Lecture Notes in Computer Science, vol 11768. Springer, Cham.}}, October 13–17, 2019, Proceedings, Part V, Shenzhen, China. \href{https://doi.org/10.1007/978-3-030-32254-0_69}{[\textcolor{blue}{online}]}
    
    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Deep learning beamformer for variable rate ultrasound imaging." in  \textit{\textbf{2019-Optics and Photonics, Wavelets and Sparsity XVIII. International Society for Optics and Photonics, 2019}}, San Diego, California, United States. 
    \href{https://arxiv.org/abs/1901.01706}{[\textcolor{blue}{online}]} \href{https://youtu.be/1pzLPKOp9ZU}{[\textcolor{blue}{video}]} [ABSTRACT-ORAL]

    \item \textbf{Shujaat Khan}, Jaeyoung Huh, and Jong Chul Ye. "Universal Deep Beamformer for Variable Rate Ultrasound Imaging." in  \textit{\textbf{2019-IEEE International Symposium on Biomedical Imaging (ISBI-2019)}}, Venice, Italy.
    \href{https://doi.org/10.13140/RG.2.2.15413.91363}{[\textcolor{blue}{online}]} [ABSTRACT-POSTER]
    
    % \item \textbf{Shujaat Khan}, Jawwad Ahmad, Alishba Sadiq, Imran Naseem, and Muhammad Moinuddin. "Spatio-Temporal RBF Neural Networks." in \textit{\textbf{2018 3rd International Conference on Emerging Trends in Engineering, Sciences and Technology (ICEEST)}}, 2018, pp. 1-5. IEEE, Karachi, Pakistan. \href{https://doi.org/10.1109/ICEEST.2018.8643322}{[\textcolor{blue}{online}]}
    
    % \item Alishba Sadiq, Muhammad Sohail Ibrahim, Muhammad Usman, Muhammad Zubair, and \textbf{Shujaat Khan}. "Chaotic Time Series Prediction using Spatio-Temporal RBF Neural Networks." in \textit{\textbf{2018 3rd International Conference on Emerging Trends in Engineering, Sciences and Technology (ICEEST)}}, 2018, pp. 1-5. IEEE, Karachi, Pakistan. \href{https://doi.org/10.1109/ICEEST.2018.8643321}{[\textcolor{blue}{online}]}
  
%   \item \textbf{Shujaat Khan}, Naveed Ahmed, Muhammad Ammar Malik, Imran Naseem, Roberto Togneri, and Mohammed Bennamoun. "FLMF: Fractional least mean fourth algorithm for channel estimation in non-Gaussian environment," in \textit{\textbf{2017 International Conference on Information and Communication Technology Convergence (ICTC)}}, 2017, pp. 466-470, Jeju Island, Korea. \href{https://doi.org/10.1109/ICTC.2017.8191021}{[\textcolor{blue}{online}]} 

    % \maxdeadcycles=200 
    \item \textbf{Shujaat Khan}, Muhammad Usman, Imran Naseem, Roberto Togneri, and Mohammed Bennamoun. "VP-FLMS: A Novel Variable Power Fractional LMS Algorithm," in \textit{\textbf{2017 Ninth International Conference on Ubiquitous and Future Networks (ICUFN)}}, 2017, pp. 290-295, Milan, Italy. \href{https://doi.org/10.1109/ICUFN.2017.7993796}{[\textcolor{blue}{online}]} 

    % \item \textbf{Shujaat Khan}, Muhammad Usman, Imran Naseem, Roberto Togneri, and Mohammad Bennamoun. "A robust variable step size fractional least mean square (RVSS-FLMS) algorithm," in \textit{\textbf{2017 IEEE 13th International Colloquium on Signal Processing \& its Applications (CSPA)}}, 2017, pp. 1-6, Batu Ferringhi, Penang Island, Malaysia. \href{https://doi.org/10.1109/CSPA.2017.8064914}{[\textcolor{blue}{online}]} 
    
    % \item Jawwad Ahmad, \textbf{Shujaat Khan}, Muhammad Usman, Imran Naseem, Muhammad Moinuddin, and Syed Hassan Jamil. "FCLMS: Fractional complex LMS algorithm for complex system identification," in \textit{\textbf{2017 IEEE 13th International Colloquium on Signal Processing \& its Applications (CSPA)}}, 2017, pp. 39-43, Batu Ferringhi, Penang Island, Malaysia. \colorbox{yellow}{[BEST PAPER AWARD]}
    % \href{https://doi.org/10.1109/CSPA.2017.8064921}{[\textcolor{blue}{online}]}  
    
    % \item Jawwad Ahmad, Muhammad Usman, \textbf{Shujaat Khan}, Imran Naseem, and Syed Hassan Jamil. "RVP-FLMS: A Robust Variable Power Fractional LMS Algorithm." in \textit{\textbf{2016 6th IEEE International Conference on Control System, Computing and Engineering (ICCSCE)}}, 2016, pp. 494-497, Batu Ferringhi, Penang Island, Malaysia.
    % \href{https://doi.org/10.1109/ICCSCE.2016.7893626}{[\textcolor{blue}{online}]}
\end{enumerate}


% \begin{cventries}

% %---------------------------------------------------------
%   \cventry
%     {} % Role
%     {Patent Applications} % Title
%     {US Patent App. US16/721,015} % Location
%     {2021} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item {Ye, Jong Chul, \textbf{Shujaat Khan} and Jaeyoung Huh. "Apparatus and method for processing ultrasound image in various sensor conditions." \textit{\textbf{US Patent App. US16/721,015 - US20210030400A1}} \href{https://patents.google.com/patent/US20210030400A1/en}{[\textcolor{blue}{online}]}}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {} % Role
%     {} % Title
%     {US Patent App. US16/721,015} % Location
%     {2021} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item Ye, Jong Chul, \textbf{Shujaat Khan} and Jaeyoung Huh. "Method for processing ultrasound image in various sensor conditions and apparatus therefor (\begin{CJK}{UTF8}{}
%         \CJKfamily{mj} 다양한 센서 조건에서의 초음파 영상 처리 장치 및 그 방법 \end{CJK})." \textit{\textbf{KR Patent App. 1020190092146 (2019.07.30)}} \href{https://doi.org/10.8080/1020190092146?urlappend=en}{[\textcolor{blue}{online}]}
%       \end{cvitems}
%     }
    
% %---------------------------------------------------------
%   \cventry
%     {} % Role
%     {} % Title
%     {US Patent App. 16/414,372} % Location
%     {2019} % Date(s)
%     {
%       \begin{cvitems} % Description(s)
%         \item {Ye, Jong Chul, Yeo Hun Yoon, \textbf{Shujaat Khan} and Jaeyoung Huh. "Image processing apparatus using neural network and method performed by image processing apparatus." \textit{\textbf{US Patent App. 16/414,372 - US20190355093A1}} \href{https://patents.google.com/patent/US20190355093A1/en}{[\textcolor{blue}{online}]}}
%       \end{cvitems}
%     }
% %---------------------------------------------------------
% \end{cventries}
