%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Deep Learning in Ultrasound Imaging} % Role
    {Siemens Healthineers} % Event
    {Princeton, U.S.A} % Location
    {May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        % \item {Introduced ultrasound imaging principles and applications.}
        \item {Introduced universal deep beamformer for medical ultrasound imaging.}
        \item {Introduced switchable and tunable beamformer.}
        \item {Introduced variational formulation of unsupervised Deep learning for ultrasound image artifact removal.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Deep Learning for Efficient Ultrasound Imaging \href{https://youtu.be/Pu3FXwctqGc}{[\textcolor{blue}{video}]}} % Role
    {Precision Electromedicince (KAIST Bio-IT Healthcare Initiative III Symposium)} % Event
    {Daejeon, S.Korea} % Location
    {Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced ultrasound imaging principles and applications.}
        % \item {Introduced deep learning technologies.}
        \item {Introduced deep learning-based variable rate beamformer for efficient ultrasound imaging.}
        \item {Introduced different applications of proposed deep learning-based beamformer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Deep learning beamformer for variable rate ultrasound imaging \href{https://youtu.be/1pzLPKOp9ZU}{[\textcolor{blue}{video}]}} % Role
    {Wavelets and Sparsity XVIII. International Society for Optics and Photonics} % Event
    {San Diego, California, U.S.A} % Location
    {Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced ultrasound imaging and deep learning technologies.}
        \item {Introduced mathematical link between adaptive beamformer and deep learning.}
        \item {Introduced variable rate beamformer for efficient ultrasound imaging.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
