%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{scriptsize}

\subsection*{Peer-Reviewed Journal Articles}
\begin{enumerate}

    \item Jaeman Shin, \textbf{Seongyong Park}, Kyucheol Shin, Wooyeong Seo, Hyunseok Kim, Doo-Kwang Kim, Bongjin Moon, Sang Gu Cha, et al. ``Temporal convolutional neural network-based feature extraction and asynchronous channel information fusion method for heart abnormality detection in phonocardiograms.'' \textit{\textbf{Computer Methods and Programs in Biomedicine}} 269, 108871 (2025).

    \item \textbf{Seongyong Park}, Sunho Kim, Peng Jiang. ``IC2Bert: masked gene expression pretraining and supervised fine tuning for robust immune checkpoint blockade (ICB) response prediction.'' \textit{\textbf{Scientific Reports}} 15, 28044 (2025).

    \item Tian-Gen Chang, \textbf{Seongyong Park}, Alejandro A.\ Sch\"affer, Peng Jiang, Eytan Ruppin. ``Hallmarks of artificial intelligence contributions to precision oncology.'' \textit{\textbf{Nature Cancer}} 6(3), 417--431 (2025).

    \item Sang-Wook Lee, \textbf{Seongyong Park}, Ji-Yeon Kim, Bongjin Moon, Dongwoo Lee, Jaewon Jang, Wooyeong Seo, Hyunseok Kim, Sung-Hoon Kim, et al. ``Impact of preanesthetic blood pressure deviations on 30-day postoperative mortality in non-cardiac surgery patients.'' \textit{\textbf{Journal of Korean Medical Science}} 39(35) (2024).

    \item \textbf{Seongyong Park}, Abdul Wahab, Muhammad Usman, Imran Naseem, Shujaat Khan. ``Artificial intelligence in bioimaging and signal processing.'' \textit{\textbf{Frontiers in Physiology}} 14, 1267632 (2023).

    \item \textbf{Seongyong Park}, Mohammad Sohail Ibrahim, Abdul Wahab, Shujaat Khan. ``GMDM: A generalized multi-dimensional distribution overlap metric for data and model quality evaluation.'' \textit{\textbf{Digital Signal Processing}} 134, 103930 (2023).

    \item Ehtisham Fazal, Mohammad Sohail Ibrahim, \textbf{Seongyong Park}, Imran Naseem, Abdul Wahab. ``Anticancer peptides classification using kernel sparse representation classifier.'' \textit{\textbf{IEEE Access}} 11, 17626--17637 (2023).

    \item \textbf{Seongyong Park}, Abdul Wahab, Minseok Kim, Shujaat Khan. ``Self-supervised learning for inter-laboratory variation minimization in surface-enhanced Raman scattering spectroscopy.'' \textit{\textbf{Analyst}} 148(7), 1473--1482 (2023).

    \item \textbf{Seongyong Park}, Gwansu Yi. ``Development of gene expression-based random forest model for predicting neoadjuvant chemotherapy response in triple-negative breast cancer.'' \textit{\textbf{Cancers}} 14(4), 881 (2022).

    \item Muhammad Usman, Shujaat Khan, \textbf{Seongyong Park}, Abdul Wahab. ``AFP-SRC: identification of antifreeze proteins using sparse representation classifier.'' \textit{\textbf{Neural Computing and Applications}} 34(3), 2275--2285 (2022).

    \item \textbf{Seongyong Park}, Jaeseok Lee, Shujaat Khan, Abdul Wahab, Minseok Kim. ``Machine learning-based heavy metal ion detection using surface-enhanced Raman spectroscopy.'' \textit{\textbf{Sensors}} 22(2), 596 (2022).

    \item \textbf{Seongyong Park}, Jaeseok Lee, Shujaat Khan, Abdul Wahab, Minseok Kim. ``SERSNet: Surface-enhanced Raman spectroscopy based biomolecule detection using deep neural network.'' \textit{\textbf{Biosensors}} 11(12), 490 (2021).

    \item Muhammad Usman, Shujaat Khan, \textbf{Seongyong Park}, Jeong-A Lee. ``AoP-LSE: antioxidant proteins classification using deep latent space encoding of sequence features.'' \textit{\textbf{Current Issues in Molecular Biology}} 43(3), 1489--1501 (2021).

    \item Yoon Hyeok Lee, Hojae Choi, \textbf{Seongyong Park}, Boah Lee, Gwansu Yi. ``Drug repositioning for enzyme modulator based on human metabolite-likeness.'' \textit{\textbf{BMC Bioinformatics}} 18(Suppl 7), 226 (2017).

    \item \textbf{Seongyong Park}, Xiaoqiang Hong, Woon Sun Choi, Taesung Kim. ``Microfabricated ratchet structure integrated concentrator arrays for synthetic bacterial cell-to-cell communication assays.'' \textit{\textbf{Lab on a Chip}} 12(20), 3914--3922 (2012).

    \item Vinuselvi Parisutham, \textbf{Seongyong Park}, Minseok Kim, Jung Min Park, Taesung Kim, Sung Kuk Lee. ``Microfluidic technologies for synthetic biology.'' \textit{\textbf{International Journal of Molecular Sciences}} 12(6), 3576--3593 (2011).

    \item Woon Sun Choi, Dogyeong Ha, \textbf{Seongyong Park}, Taesung Kim. ``Synthetic multicellular cell-to-cell communication in inkjet printed bacterial cell systems.'' \textit{\textbf{Biomaterials}} 32(10), 2500--2507 (2011).

    \item \textbf{Seongyong Park}, Dasol Kim, Robert J.\ Mitchell, Taesung Kim. ``A microfluidic concentrator array for quantitative predation assays of predatory microbes.'' \textit{\textbf{Lab on a Chip}} 11(17), 2916--2923 (2011).

\end{enumerate}

\subsection*{Conference Proceedings}
\begin{enumerate}
    \item \textbf{Seongyong Park}, Shujaat Khan, Muhammad Moinuddin, Ubaid M.\ Al-Saggaf. ``GSSMD: A new standardized effect size measure to improve robustness and interpretability in biological applications.'' \textit{\textbf{IEEE International Conference on Bioinformatics and Biomedicine (BIBM)}}, pp.\ 1096--1099 (2020).
\end{enumerate}

\subsection*{Preprints}
\begin{enumerate}
    \item \textbf{Seongyong Park}, Shujaat Khan, Abdul Wahab. ``E3-targetPred: Prediction of E3-target proteins using deep latent space encoding.'' \textit{arXiv:2007.12073} (2020).
    \item \textbf{Seongyong Park}, Shujaat Khan. ``GSSMD: New metric for robust and interpretable assay quality assessment and hit selection.'' \textit{arXiv:2001.06384} (2020).
\end{enumerate}

\subsection*{Patents}
\begin{enumerate}
    \item Bumki Min, Gwansu Yi, \textbf{Seongyong Park}. ``System and method for disease prediction based on group marker consisting of genes having similar function.'' \textit{\textbf{KR Patent 10-2236194}}, issued 30 March 2021.
    \item Taesung Kim, \textbf{Seongyong Park}. ``Microfluidic concentrator for communication assays of microbes.'' \textit{\textbf{KR Patent 10-1330473}}, issued 4 February 2013.
    \item Taesung Kim, \textbf{Seongyong Park}. ``Microfluidic concentrator array for observing predation behavior of microbes.'' \textit{\textbf{KR Patent 10-1238556}}, issued 22 February 2013.
\end{enumerate}

\subsection*{Software}
\begin{enumerate}
    \item \textbf{SecActPy} --- Python package for secreted-protein activity inference from bulk and single-cell gene expression. \href{https://github.com/psychemistz/SecActPy}{github.com/psychemistz/SecActPy}
    \item \textbf{spatial-gpu} --- GPU-accelerated spatial kernels for neighborhood activity inference on spatial transcriptomics. \href{https://github.com/psychemistz/spatial-gpu}{github.com/psychemistz/spatial-gpu}
    \item \textbf{RidgeR} --- R package for ridge-regression-based activity inference. \href{https://github.com/psychemistz/RidgeR}{github.com/psychemistz/RidgeR}
\end{enumerate}

\end{scriptsize}
